\section{Using SCORE to Initialize Local Optimization}
\label{sec:score-to-initialize}

Though SCORE can be solved to global optimality, in general the SCORE solution
will differ from that of the original problem due to the relaxed constraints.
This is not a serious limitation, as the intent is that the SCORE solution will
be close to the solution of the original problem. If true, the SCORE solution
can be projected to the feasible set of the original problem, and thereby serve
as a robust and principled initialization procedure.

Projecting the SCORE solution to the original problem's feasible set only
involves the estimated rotations. As SCORE relaxes the $\SOd$ constraints, the
estimated values, $\rot_i$, will generally not be valid rotation matrices. As in
\cite{martinec07cvpr}, we project the approximate rotation estimates to the
nearest rotation matrix via singular value decomposition, as follows:
\begin{align}
    & \orot_i = \argmin_{\rot_i}~~\lVert \rot_i - \erot_{i,approx} \rVert_F^2 \label{eq:single-rotation-frob} \\
    & U,S,V^\top = \SVD(\erot) \label{eq:SVD} \\
    & \orot_i = U ~ \diag([1, 1, \det(U V^\top)]) ~ V^\top \label{eq:SOd-projection}
\end{align}
Projecting all approximate rotations to $\SOd$ produces a valid set of pose and
landmark estimates. We then use this projected solution to initialize the MAP
problem in Prob. \ref{prob:ra-slam-nls} and solve the problem with an iterative,
local-search based NLS solver (e.g., \cite{dellaert2012techreport}) to refine
the SCORE initial estimate.